RIScatter: Unifying\\Backscatter Communications, Symbiotic Radio, and Reconfigurable Intelligent Surface

### 2022-09-03 main.tex
:pencil: Update discussion on coding

		\emph{First,} we propose RIScatter nodes to adapt the input probability distribution of a finite-state passive scatter device based on link priority and \gls{csi}.
		The reflection pattern over time is no longer fully random or deterministic, but can be flexibly distributed to unify and balance backscatter modulation with passive beamforming.
		Scattering source of \gls{bc}/\gls{sr} and reflecting element of \gls{ris} can be regarded as its extreme cases, where the input distribution boils down to equiprobable and degenerate, respectively.
		Like aforementioned \gls{ris}-empowered \gls{bc}/\gls{sr} schemes, the passive nodes require regular coordination with active devices, but the advantages are 1) RIScatter nodes can be built over conventional load-switching scatterers instead of composite metamaterial; 2) the optimization cost of input distribution is much lower than that of \gls{ris} reflection coefficients; 3) adaptive backscatter channel coding can exploit \gls{csi} to achieve higher instantaneous rate than conventional uncoded transmission; 4) the potentially dispersed characteristics of RIScatter nodes (and legacy users) avoids the development optimization and allows uniformly good performance for both links.

@@

		\emph{Fifth,} we provide numerical results to demonstrate the benefits of RIScatter and proposed algorithms.
		It is concluded that 1) RIScatter nodes provide flexible transmit-assist tradeoff using adaptive input distribution design; 2) when primary link is absolutely prioritized, the input probability of each node is \num{1} at one state and \num{0} at the others, which coincides with discretized \gls{ris}; 3) when backscatter link is absolutely prioritized, RIScatter nodes can exploit adaptive channel coding to achieve higher instantaneous rate than uncoded equiprobable inputs of \gls{bc}/\gls{sr}; 4) the proposed \gls{kkt} input distribution design converges to stationary points, whose average performance is very close to global optimal; 5) the proposed \gls{pgd} beamforming provides larger rate region than \gls{mrt}-based schemes; 6) the decision region schemes adapted to input distribution provide higher backscatter rates than the non-adaptive \gls{ml} detector; 7) cooperation between passive nodes in terms of joint encoding can further boost the total backscatter rate; 8) the low complexity of input distribution design and the marginal effect of increasing reflection states motivates the use of low-order scattering nodes to replace high-resolution \gls{ris}.
	\end{subsection}

@@

\begin{section}{RIScatter}
	Using shared spectrum, energy and infrastructures, RIScatter is a novel passive communication/assistance protocol that generalizes \gls{bc}, \gls{sr} and \gls{ris} from the perspective of input distribution.
	In particular, the potentially dispersed passive RIScatter nodes ride over an active legacy transmission in a flexible and mutualistic manner, while the practical RIScatter receiver cooperatively decodes both primary and backscatter links under the benefits of backscatter modulation and passive beamforming.
	% TODO compare BC, SR and IRS
	\begin{subsection}{RIScatter Nodes}
		Based on link priority and \gls{csi}, RIScatter nodes adapt the \emph{state input probability distribution} of antenna-based scatterers to unify backscatter modulation and passive beamforming.
		The scattering sources of \gls{bc}/\gls{sr} and reflecting elements of \gls{ris} can be viewed as its extreme cases, where the input distribution boils down to equiprobable and degenerate, respectively.
		\begin{figure}[!t]
			\centering
			\subfloat[Input Distribution]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/illustration/input_distribution.tex}
				}
				\label{fi:input_distribution}
			}
			\\
			\subfloat[Time Block]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/illustration/time_block.tex}
				}
				\label{fi:time_block}
			}
			\caption{
				Input probability distribution and time block structure of \gls{bc}, \gls{sr}, \gls{ris}, and RIScatter.
				$T_s$ and $T_c$ respectively denote the primary and backscatter symbol period.
				Within channel coherence time, RIScatter nodes semi-randomly select reflection state for each backscatter symbol block under the guidance of input probability distribution.
			}
			\label{fi:riscatter_distribution}
		\end{figure}
		As illustrated in Fig. \ref{fi:riscatter_distribution}, instead of always using fully random or deterministic reflection pattern over time, each RIScatter node can \emph{flexibly adjust} its input distribution to balance information encoding and channel reconfiguration.
		That is, it semi-randomly select the reflection state per backscatter symbol block under the guidance of input probability $P(\Gamma_m)$ for state $m$.
		Such an adaptive backscatter channel coding coincides with \gls{ris} when primary link is absolutely prioritized, and outperforms the uncoded equiprobable inputs of \gls{bc}/\gls{sr} when backscatter link is absolutely prioritized.
		Besides, the dispersed characteristics of RIScatter nodes (and legacy users) avoids the development optimization and allows uniformly good performance for both links.

@@

	\begin{subsection}{Input Distribution versus Link Priority}
		\begin{figure}[!t]
			\centering
			\subfloat[Instance 1\label{fi:distribution_weights_1}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/distribution_weights_1.tex}
				}
			}
			\subfloat[Instance 2\label{fi:distribution_weights_2}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/distribution_weights_2.tex}
				}
			}
			\caption{Typical instances of node input distribution for different weights.}
			\label{fi:distribution_weights}
		\end{figure}
		The objective of this study is to demonstrate each RIScatter node can adjust its input distribution based on \gls{csi} and link priority to balance backscatter modulation and passive beamforming.
		For this aim, we evaluate the \gls{kkt} input distribution by Algorithm \ref{al:input_distribution} for a single node under different weights $\rho=\{0,0.1,0.2,0.3,1\}$ in Fig. \ref{fi:distribution_weights}, where \subref*{fi:distribution_weights_1} and \subref*{fi:distribution_weights_2} are two representative instances.
		We observe that as $\rho$ increases from \num{0} to \num{1}, the \gls{kkt} input distribution
		gradually progresses from slightly skewed to completely biased.
		For $\rho=0$ where backscatter performance is absolutely prioritized, the \gls{csi}-adaptive channel coding at the RIScatter node provides higher backscatter rate than conventional \gls{bc} and \gls{sr} nodes with uncoded equiprobable inputs, and some states may end up unused since they cannot produce enough energy difference over the existing alphabet.
		On the other hand, for $\rho=1$ where primary performance is absolutely prioritized, the input probability is \num{1} at the state that maximizes the primary equivalent channel strength, and \num{0} at the others.
		In this case, the reflection pattern over time is fully deterministic, and the RIScatter node indeed boils down to a \gls{ris} element with discrete phase shifts.
		Those observations meet our s that RIScatter nodes include scattering sources of \gls{bc}/\gls{sr} and reflecting elements of \gls{ris} as special cases, and generalize backscatter modulation and passive beamforming from the perspective of input distribution design.
		For the \gls{bcd} algorithm, we choose the \gls{kkt} input distribution by Algorithm \ref{al:input_distribution}, the \gls{pgd} active beamforming by Algorithm \ref{al:active_beamforming}, and the \gls{smawk} decision threshold by \cite{He2021} as reference.
	\end{subsection}

>>>>

		\emph{First,} we propose RIScatter nodes to adapt the input probability distribution of a finite-state passive scatter device based on link priority and \gls{csi}.
		The reflection pattern over time is no longer fully random or deterministic, but can be flexibly distributed to unify and balance backscatter modulation with passive beamforming.
		Scattering source of \gls{bc}/\gls{sr} and reflecting element of \gls{ris} can be regarded as its extreme cases, where the input distribution boils down to equiprobable and degenerate, respectively.
		Like aforementioned \gls{ris}-empowered \gls{bc}/\gls{sr} schemes, the passive nodes require regular coordination with active devices, but the advantages are 1) RIScatter nodes can be built over conventional load-switching scatterers instead of composite metamaterial; 2) the optimization cost of input distribution is much lower than that of \gls{ris} reflection coefficients; 3) adaptive backscatter channel coding can exploit \gls{csi} to achieve higher instantaneous rate than conventional equiprobable line coding in \gls{bc}/\gls{sr}; 4) the potentially dispersed characteristics of RIScatter nodes (and legacy users) avoids the development optimization and allows uniformly good performance for both links.

@@

		\emph{Fifth,} we provide numerical results to demonstrate the benefits of RIScatter and proposed algorithms.
		It is concluded that 1) RIScatter nodes provide flexible transmit-assist tradeoff using adaptive input distribution design; 2) when primary link is absolutely prioritized, the input probability of each node is \num{1} at one state and \num{0} at the others, which coincides with discretized \gls{ris}; 3) when backscatter link is absolutely prioritized, RIScatter nodes can exploit adaptive channel coding to achieve higher instantaneous rate than conventional equiprobable inputs of \gls{bc}/\gls{sr}; 4) the proposed \gls{kkt} input distribution design converges to stationary points, whose average performance is very close to global optimal; 5) the proposed \gls{pgd} beamforming provides larger rate region than \gls{mrt}-based schemes; 6) the decision region schemes adapted to input distribution provide higher backscatter rates than the non-adaptive \gls{ml} detector; 7) cooperation between passive nodes in terms of joint encoding can further boost the total backscatter rate; 8) the low complexity of input distribution design and the marginal effect of increasing reflection states motivates the use of low-order scattering nodes to replace high-resolution \gls{ris}.
	\end{subsection}

@@

\begin{section}{RIScatter}
	Using shared spectrum, energy and infrastructures, RIScatter is a novel passive communication/assistance protocol that generalizes \gls{bc}, \gls{sr} and \gls{ris} from the perspective of input distribution.
	In particular, the potentially dispersed passive RIScatter nodes ride over an active legacy transmission in a flexible and mutualistic manner, while the practical RIScatter receiver cooperatively decodes both primary and backscatter links under the benefits of backscatter modulation and passive beamforming.
	% TODO compare BC, SR and IRS
	\begin{subsection}{RIScatter Nodes}
		Based on link priority and \gls{csi}, RIScatter nodes adapt the \emph{state input probability distribution} of antenna-based scatterers to unify backscatter modulation and passive beamforming.
		Conventional line-coded \gls{bc}/\gls{sr} nodes (e.g., EPC Gen 2 UHF \gls{rfid} using FM0) and deterministic \gls{ris} elements can be viewed as its extreme cases, where the input distribution boils down to equiprobable and degenerate, respectively.
		\begin{figure}[!t]
			\centering
			\subfloat[Input Distribution]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/illustration/input_distribution.tex}
				}
				\label{fi:input_distribution}
			}
			\\
			\subfloat[Time Block]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/illustration/time_block.tex}
				}
				\label{fi:time_block}
			}
			\caption{
				Input probability distribution and time block structure of \gls{bc}, \gls{sr}, \gls{ris}, and RIScatter.
				$T_s$ and $T_c$ respectively denote the primary and backscatter symbol period.
				Within channel coherence time, RIScatter nodes semi-randomly select reflection state for each backscatter symbol block under the guidance of input probability distribution.
			}
			\label{fi:riscatter_distribution}
		\end{figure}
		As illustrated in Fig. \ref{fi:riscatter_distribution}, instead of always using fully random or deterministic reflection pattern over time, each RIScatter node can \emph{flexibly adjust} its input distribution to balance information encoding and channel reconfiguration.
		That is, it semi-randomly select the reflection state per backscatter symbol block under the guidance of input probability $P(\Gamma_m)$ for state $m$.
		Such an adaptive backscatter channel coding coincides with \gls{ris} when primary link is absolutely prioritized, and outperforms the conventional equiprobable line-coded \gls{bc}/\gls{sr} when backscatter link is absolutely prioritized.
		Besides, the dispersed characteristics of RIScatter nodes (and legacy users) avoids the development optimization and allows uniformly good performance for both links.

@@

	\begin{subsection}{Input Distribution versus Link Priority}
		\begin{figure}[!t]
			\centering
			\subfloat[Instance 1\label{fi:distribution_weights_1}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/distribution_weights_1.tex}
				}
			}
			\subfloat[Instance 2\label{fi:distribution_weights_2}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/distribution_weights_2.tex}
				}
			}
			\caption{Typical instances of node input distribution for different weights.}
			\label{fi:distribution_weights}
		\end{figure}
		The objective of this study is to demonstrate each RIScatter node can adjust its input distribution based on \gls{csi} and link priority to balance backscatter modulation and passive beamforming.
		For this aim, we evaluate the \gls{kkt} input distribution by Algorithm \ref{al:input_distribution} for a single node under different weights $\rho=\{0,0.1,0.2,0.3,1\}$ in Fig. \ref{fi:distribution_weights}, where \subref*{fi:distribution_weights_1} and \subref*{fi:distribution_weights_2} are two representative instances.
		We observe that as $\rho$ increases from \num{0} to \num{1}, the \gls{kkt} input distribution
		gradually progresses from slightly skewed to completely biased.
		For $\rho=0$ where backscatter performance is absolutely prioritized, the \gls{csi}-adaptive channel coding at the RIScatter node provides higher backscatter rate than conventional \gls{bc} and \gls{sr} nodes with equiprobable inputs, and some states may end up unused since they cannot produce enough energy difference over the existing alphabet.
		On the other hand, for $\rho=1$ where primary performance is absolutely prioritized, the input probability is \num{1} at the state that maximizes the primary equivalent channel strength, and \num{0} at the others.
		In this case, the reflection pattern over time is fully deterministic, and the RIScatter node indeed boils down to a \gls{ris} element with discrete phase shifts.
		Those observations meet our s that RIScatter nodes include scattering sources of \gls{bc}/\gls{sr} and reflecting elements of \gls{ris} as special cases, and generalize backscatter modulation and passive beamforming from the perspective of input distribution design.
		For the \gls{bcd} algorithm, we choose the \gls{kkt} input distribution by Algorithm \ref{al:input_distribution}, the \gls{pgd} active beamforming by Algorithm \ref{al:active_beamforming}, and the \gls{smawk} decision threshold by \cite{He2021} as reference.
	\end{subsection}
